---
title: "STAT331 Data Visualizations and Dashboards - Assignment 2"
author: "Andrew Sparkes"
date: "2025-10-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE, include=FALSE}
library(tidyverse)
library(readr)
library(magrittr) # for %>%
library(ggplot2) # mpg dataset and plotting
library(reticulate) # for calling python
library(tigris) # for states data
library(sf) # simple features
library(ggrepel) # for repelling labels off of one another
```

Using data from the Monthly Treasury Datasets create plots with ggplot2 that meet the following requirements:

1.)  You must create 2 plots

2.)  The plots must use two different plot types (boxplot and scatterplot, bar-plot and radar-plot, etc...)

3.)  The plots must encode the data using geometries and aesthetics that follow the best practices that we learned in class.

(You are not required to work with axis labels, titles, customized legends, etc... yet.  We will work on theming next week.)

Submit

1.)  Code

2.)  Plot

3.)  A description of the intent of the plot and what the user should get from looking at the plot.

```{r load_dataset}
MTS <- read_csv("MTS_AgcyInvest_20150331_20250930.csv")

```