---
title: "STAT331 Data Visualizations and Dashboards - Assignment 2"
author: "Andrew Sparkes"
date: "2025-10-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE, include=FALSE}
library(tidyverse)
library(readr)
library(magrittr) # for %>%
library(ggplot2) # mpg dataset and plotting
library(reticulate) # for calling python
library(tigris) # for states data
library(sf) # simple features
library(ggrepel) # for repelling labels off of one another
library(scales) # for comma-tizing the y tick labels
```

Using data from the Monthly Treasury Datasets create plots with ggplot2 that meet the following requirements:

1.)  You must create 2 plots

2.)  The plots must use two different plot types (boxplot and scatterplot, bar-plot and radar-plot, etc...)

3.)  The plots must encode the data using geometries and aesthetics that follow the best practices that we learned in class.

(You are not required to work with axis labels, titles, customized legends, etc... yet.  We will work on theming next week.)

Submit

1.)  Code

2.)  Plot

3.)  A description of the intent of the plot and what the user should get from looking at the plot.

```{r load_datasets, include = FALSE}
# for now, loading /all/ the data
MTS_AgcyInvest <- readr::read_csv("MTS_AgcyInvest_20150331_20250930.csv")
#readr::spec(MTS_AgcyInvest)
MTS_AgcyIssue <- readr::read_csv("MTS_AgcyIssue_20150331_20250930.csv")
#readr::spec(MTS_AgcyIssue)
MTS_AgcySpecIssue <- readr::read_csv("MTS_AgcySpecIssue_20150331_20250930.csv")
#readr::spec(MTS_AgcySpecIssue)
MTS_BudsRsltFin <- readr::read_csv("MTS_BudRsltFin_20150331_20250930.csv")
#readr::spec(MTS_BudsRsltFin)
MTS_ChgExcsLiab <- readr::read_csv("MTS_ChgExcsLiab_20150331_20250930.csv")
#readr::spec(MTS_ChgExcsLiab)
MTS_FinDfctDispSur <- readr::read_csv("MTS_FinDfctDispSur_20150331_20250930.csv")
#readr::spec(MTS_FinDfctDispSur)
MTS_GuarDirLoan <- readr::read_csv("MTS_GuarDirLoan_20150331_20250930.csv")
#readr::spec(MTS_GuarDirLoan)
MTS_OutlyAgcy <- readr::read_csv("MTS_OutlyAgcy_20150331_20250930.csv")
#readr::spec(MTS_OutlyAgcy)
MTS_RcptOutlyDfctSur <- readr::read_csv("MTS_RcptOutlyDfctSur_20150331_20250930.csv")
#readr::spec(MTS_RcptOutlyDfctSur)
MTS_RcptOutlyMo <- readr::read_csv("MTS_RcptOutlyMo_20150331_20250930.csv")
#readr::spec(MTS_RcptOutlyMo)
MTS_RcptSrc <- readr::read_csv("MTS_RcptSrc_20150331_20250930.csv")
#readr::spec(MTS_RcptSrc)
MTS_RcptSrcOutlyAgcy <- readr::read_csv("MTS_RcptSrcOutlyAgcy_20150331_20250930.csv")
#readr::spec(MTS_RcptSrcOutlyAgcy)
MTS_RcptSrcOutlyFcn <- readr::read_csv("MTS_RcptSrcOutlyFcn_20150331_20250930.csv")
#readr::spec(MTS_RcptSrcOutlyFcn)
MTS_TrustFund <- readr::read_csv("MTS_TrustFund_20150331_20250930.csv")
#readr::spec(MTS_TrustFund)
```




```{r cleanup_and_mangle}
# first, let's figure out what the hell we even want to look at in this enormous dataset

# let's start with the inclass example, looking at the DoJ's transactions
MTS_AgcyInvest_CumSumTrans <- MTS_AgcyInvest %>%
  filter(`Classification Description` == "Department of Justice") %>%
  select(`Record Date`, `Classification Description`, `Current Month Net Transaction Amount`, `Fiscal Year to Date Net Transaction Amount`)  %>%
  mutate(Cumulative.Transaction = cumsum(`Current Month Net Transaction Amount`)) %>%
  rename(Record.Date = `Record Date`) %>% # TODO probably better way to do this in a batch
  rename(Classification.Description = `Classification Description`) %>%
  rename(Current.Month.Net.Transaction.Amount = `Current Month Net Transaction Amount`) %>%
  rename(Fiscal.Year.to.Date.Net.Transaction.Amount = `Fiscal Year to Date Net Transaction Amount`)

```

```{r plot_the_stuff_part_one}

plot1 <- MTS_AgcyInvest_CumSumTrans %>% 
  ggplot() +
  geom_line(aes(x = Record.Date, y = Cumulative.Transaction), color="red", linewidth = 3) + # TODO fix this, make it beautiful
  theme_dark() +
  xlab("Date") +
  ylab("Current Balance (USD)") +
  scale_y_continuous(label=comma, limits=c(min(MTS_AgcyInvest_CumSumTrans$Cumulative.Transaction), 
                                           max(MTS_AgcyInvest_CumSumTrans$Cumulative.Transaction)))

plot1
```


```{r}
# TODO plot 2
```