---
title: "STAT331 Data Visualizations and Dashboards - Assignment 3"
author: "Andrew Sparkes"
date: "2025-10-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Find your dataset that you plan to use for your project in this course.

Your project will be to create a shiny dashboard, so you will need to identify a dataset that is complex enough that you can create a dashboard with some interesting graphics.

For this assignment, you will create the following.

1.)  Code your own customized theme that you can apply to your graphs in order to standardize their appearance.

2.)  Three (3) different graphs which demonstrate important characteristics of your data.
These graphs need to follow the best practices described in class.

```{r load_packages, echo=FALSE, include=FALSE}
library(tidyverse)
library(magrittr) # for %>%
library(ggplot2) # mpg dataset and plotting
library(reticulate) # for calling python
library(tigris) # for states data
library(readr)
library(sf) # simple features
library(ggrepel) # for repelling labels off of one another
```




```{r load_dataset, include = FALSE}
MH_Data <- readr::read_csv("Mental_Health_Dataset.csv")
readr::spec(MH_Data)
```

```{r tidy_data, include = FALSE}

```