---
title: "Assignment 5"
author: "Andrew Sparkes"
date: "2025-11-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 5

Your task for this assignment will be to use the data provided to create a dynamic report.  
The example report shows data for NKE, but the dataset has multiple stocks in it.  You need
to produce two things:

1.  A .R file which can be used to call the report
2.  A .Rmd file which can use the parameterized report to produce the report you see.  

You do not need the bottom section of the report that gives you an interpretation of the data.  That is present so that you 
can create the graphs.  

*Note:  Both the data format and the graphs on this assignment are pretty difficult to deal with.  Please do your best to match them in format, but some minor alterations 
may be appropriate.  One of the geom_xxx options used has not been introduced in class and will require some exploration.



```{r, load_packages, echo = FALSE, include = FALSE}
# Load packages
library(tidyverse)
library(rmarkdown)

```

```{r}
render(
     input = "Report.Rmd",
     output_file = "AAPL.html",
     params = list(symbol = "AAPL")
)
```

```{r}
render(
     input = "Report.Rmd",
     output_file = "DIS.html",
     params = list(symbol = "DIS")
)
```

```{r}
render(
     input = "Report.Rmd",
     output_file = "NKE.html",
     params = list(symbol = "NKE")
)
```

## Create a vector of all states and the District of Columbia
#state <- tibble(state.name) %>%
#     rbind("District of Columbia") %>%
#     pull(state.name)

## Create a tibble with information on the:
## input R Markdown document
## output HTML file
## parameters needed to knit the document
#reports <- tibble(
#     input = "AutomatedReport.Rmd",
#     output_file = str_glue("{state}.html"),
#     params = map(state, ~ list(state = .))
#)

## Generate all of our reports
#pwalk(reports, render)
