---
title: "`r params$symbol` Financial Report"         
subtitle: "Financial Overview"
author: "Andrew Sparkes"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
params:
  symbol: 
    label: "Symbol"
    value: NKE
    input: select
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  # suppress only warnings and messages
  echo = TRUE,
  warning = TRUE, # for now
  message = TRUE # for now
)
```


```{r load_packages, echo = FALSE, include = FALSE}
library(tidyverse)
library(tibble)
library(dplyr)
library(ggplot2)
library(ggstance)
```

```{r load_dataset_and_mangle, include = FALSE}
# first, load in the first row, the df headers
data_headers <- readr::read_table("homework_5_data.csv", n_max = 1) # read_table because it's whitespace-delimited, ew
# readr::spec(data_headers)

# read remainder of the data, skipping the header row and the partially blank 2nd row
data <- readr::read_table("homework_5_data.csv", skip = 2, col_names = as.character(colnames(data_headers))) |>
  select(-1) # select all but first col (drop the unnamed id col) NOTE: select() drops the table spec, so it loses the col names...
# readr::spec(data) # returns NULL... TODO look into this behavior


# set the col names of the dataset to the headers extracted above, removing the double quotes
colnames(data) <- gsub("\"", "", colnames(data_headers), fixed = TRUE)

# remove double quotes from the Company col
data$Company <- gsub("\"", "", data$Company, fixed = TRUE)

# convert from tibble to data.frame
data <- as.data.frame(data)
```


## Report on the Overall Status of `r params$symbol`


```{r manipulate_some_data, include = FALSE}
# now that the whole dataset has been wrangled, let's filter it down to just the relevant symbol info, then we'll pivot it by the date columns to long format and store for later plotting
pivoted_data <- data |>
  filter(`Company` == params$symbol) |>
  pivot_longer(
    cols = matches("[0-9]{4}-[0-9]{2}-[0-9]{2}"), # YYYY-MM-DD regex
    names_to = "Date",
    values_to = "Value",
    names_prefix = ""
  )
df_to_graph <- pivoted_data |>
  select(-Company, -Forward_PE_Ratio, -PEG_Ratio, -Price_Sales_Ratio, -Price_Book_Ratio, -EV_REV_Ratio, -EV_EBITDA_Ratio) |> # pruning off the data that isn't needed for plotting (incl. Company, leaving just Date and Value)
  mutate(Date = as.Date(Date)) # force Date col as Date type
```


```{r make_the_line_chart_happen}
# line chart of stock price by date
df_to_graph |> ggplot(aes(x = Date, y = Value)) +
  geom_line() + # make pretty line
  geom_point() + # add points on actual data points
  labs(x = "Date", y = paste(params$symbol, "Price", sep = " ")) +
  scale_x_date(date_breaks = "10 day", date_labels = "%D") + # breaks every 10d, with labels YYYY-MM-DD
  theme_dark()
```

```{r make_the_financial_ratios_happen, include = FALSE}
# financial ratios

fin_ratios <- pivoted_data |>
  select(Company, Forward_PE_Ratio, PEG_Ratio, Price_Sales_Ratio, Price_Book_Ratio, EV_REV_Ratio, EV_EBITDA_Ratio) |>
  distinct()
```

```{r plot_the_financial_ratios}
# first plot is PE ratio and EV_EBITDA

# prune off the first two values we want to plot
PE_EV_data <- fin_ratios |>
  select(Forward_PE_Ratio, EV_EBITDA_Ratio)

# dump them in a vector
v <- c(PE_EV_data["Forward_PE_Ratio"], PE_EV_data["EV_EBITDA_Ratio"])

# make a df of the data to plot
df <- data.frame(
  id    = factor(c("Forward PE Ratio", "EV/EBITDA Ratio")),
  min   = c(15, 6),
  value = c(v$Forward_PE_Ratio, v$EV_EBITDA_Ratio),
  max   = c(25, 20)
)


# Build the plot
box_thickness <- 0.8
PE_EV_plot <- df |>
  ggplot(
    aes(y = id, # represents the type of financial ration: PE, EV, etc
        xmin = 1,
        xmax = 10
    )
  ) +

  # Box spanning min to max
  geom_rect(
    aes(
      xmin = min,
      xmax = max,
      ymin = as.numeric(id) - box_thickness / 2,
      ymax = as.numeric(id) + box_thickness / 2
    ),
    fill = "lightgray",
    color = "darkgray"
  ) +

  # Horizontal pointrange for min to max with a point at value
  geom_pointrangeh(
    aes(
      x = value, 
      xmin = min,
      xmax = max
    ),
    size = 1.1,
    color = "blue"
  ) +
  labs(
    x = "Metric",
    y = "",
    title = "Forward PE and EV/EBITDA Ratios"
  ) +
  theme_minimal()
PE_EV_plot
```


```{r plot_the_other_stuff}

# prune off the first two values we want to plot
PS_PB_PEG_EVREV_data <- fin_ratios |>
  select(Price_Sales_Ratio, Price_Book_Ratio, PEG_Ratio, EV_REV_Ratio)

# dump them in a vector
v <- c(PS_PB_PEG_EVREV_data["Price_Sales_Ratio"], PS_PB_PEG_EVREV_data["Price_Book_Ratio"],  PS_PB_PEG_EVREV_data["PEG_Ratio"],  PS_PB_PEG_EVREV_data["EV_REV_Ratio"])

# make a df of the data to plot
df <- data.frame(
  id    = factor(c("Price Sales Ratio", "Price Book Ratio", "PEG Ratio", "EV/REV Ratio")),
  min   = c(1, 1, 0.5, 1),
  value = c(v$Price_Sales_Ratio, v$Price_Book_Ratio, v$PEG_Ratio, v$EV_REV_Ratio),
  max   = c(3, 3, 1.5, 3)
)


# Build the plot
box_thickness <- 0.8
PS_PB_PEG_EVREV_plot <- df |>
  ggplot(
    aes(y = id, # represents the type of financial ration: PE, EV, etc
        xmin = 1,
        xmax = 10
    )
  ) +

  # Box spanning min to max
  geom_rect(
    aes(
      xmin = min,
      xmax = max,
      ymin = as.numeric(id) - box_thickness / 2,
      ymax = as.numeric(id) + box_thickness / 2
    ),
    fill = "lightgray",
    color = "darkgray"
  ) +

  # Horizontal pointrange for min to max with a point at value
  geom_pointrangeh(
    aes(
      x = value, 
      xmin = min,
      xmax = max
    ),
    size = 1.1,
    color = "blue"
  ) +
  labs(
    x = "Metric",
    y = "",
    title = "Price Sales, Price Book, PEG, EV/REV Ratios"
  ) +
  theme_minimal()
PS_PB_PEG_EVREV_plot
```

P/E Forward

Definition: The P/E Forward ratio compares a company’s current share price to its expected earnings per share over the next 12 months. It helps investors assess valuation based on future profitability.

Typical Range:
- < 15: Undervalued or mature
- 15–25: Fairly valued
- > 25: High growth expectations
PEG Ratio

Definition: The PEG ratio adjusts the P/E ratio by factoring in expected earnings growth, offering a more nuanced valuation. Typical Range:
- < 1: Undervalued
- ≈ 1: Fairly valued
- > 1: Overvalued
Price/Sales

Definition: This ratio compares a company’s market capitalization to its total revenue. It’s useful for evaluating companies with little or no earnings.
Typical Range:
- < 1: Undervalued
- 1–3: Reasonable
- > 3: High expectations
Price/Book

Definition: The P/B ratio compares market value to book value, indicating how much investors are willing to pay for net assets.

Typical Range:
- < 1: Possibly undervalued
- 1–3: Normal
- > 3: Premium valuation
EV/Revenue

Definition: This ratio compares a company’s total value (including debt) to its revenue. It’s useful for comparing companies with different capital structures.

Typical Range:
- < 1: Undervalued
- 1–3: Reasonable
- > 3: High growth expectations
EV/EBITDA

Definition: EV/EBITDA measures a company’s total value relative to its earnings before interest, taxes, depreciation, and amortization. It’s widely used for valuation across industries.

Typical Range:
- < 6: Undervalued
- 6–12: Fair
- > 20: High growth or overvalued


